\vspace{-.2in} Squint: Lossy Hierarchical Compression on Symbol Streams \vspace{-.1in}

### 2012-12-12 tex/paper.tex
Concussion

\subsection{Summary of Results}

* General concept of simplifying grammars, two proposed algorithms
* reasonably efficient implementation with runtime better than expected
* compared algorithms, evaluated effectiveness of reducer
* looked at effect of epsilon

\subsection{Ratios and Fidelity}

* How useful are these algorithms??
* What is the ratio we get
* What kind of fidelity to we get

>>>>

In this paper, we present the design and implementation of original algorithms
for performing lossy compression of hierarchical data.  To our knowledge, the
idea of lossifying context-free grammar as a means of simplifying and
compressing hierarchical structure has not been explored in the past.  We
believe, however, that it is a technique worth further investigation.

We were able to produce a reasonably efficient implementation of two basic
grammar lossification algorithms, and in particular, the runtime for our
\Cluster was better than we expected.  Our techniques resulted in good
compression ratios.  The fidelity of the output strings from our compressed
grammars, as compared to the original inputs, were lacking---however, our
techniques were intended not to maintain the fidelity of outputs, but rather,
of hierarchical structure.

Unfortunately, we were unable to establish numerical metrics for the structural
similarities between the lossless and lossy grammars; however, subjectively, we
find that lossification maintains interesting invariants, such as the word
``God'' in a lossy compression of the Bible, or the texture and block structure
of an obfuscated C program.
